SciPy - some descriptive title here

### 2018-05-22 scipy-1.0/paper.tex
ENH: add draft of test suite section.

>>>>

    \subsubsection*{Test suite}
    The SciPy test suite is orchestrated by a continuous integration matrix
    that includes posix and Windows (32/64-bit) platforms managed by Travis CI and appveyor,
    respectively. Our tests cover Python versions 2.7, 3.4, 3.5, 3.6, and include
    code linting with pyflakes and pycodestyle. There are more than $13000$ unit
    tests in the test suite, which is written for usage with the pytest runner, and
    with a 76.5 \% coverage of approximately $204000$ lines
    of code. Documentation for the code is automatically built and hosted by the
    CircleCI service to facilitate evaluation of documentation changes / integrity.
    Our full test suite also passes with PyPy3, a just-in-time compiled version
    of the Python language.
    % NOTE: is there a citation for PyPy?
